Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-10 paper/main.tex
some changes to report of individual results

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort.
%
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different cognitive and perceptual
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways of processing
different kind of visual information:
% dorsal vs ventral pathway
a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
ventral pathway that leads into into the temporal lobe (the ``what pathway'')
\citep{goodale1992separat, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus is not anatomically but
functionally defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

\todo[inline]{contrasts are mentioned in the method section for the purpose of
completeness. Shall results be reported (and later discussed)?}

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
corrected) can be found in the accompanying dataset.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (transversal
slice z=-11 for all subjects was chosen as it depicts voxels of significant
clusters in almost all subjects).

@@

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
12 of 14 subjects and a unilateral right clusters in two subjects (sub-04,
sub-20).
% procedure in Sengupta
Individual ROIs were assessed by visually inspecting unthresholded $z$-maps of
three different contrasts, and setting a subjectively best fitting $z$-threshold
to isolate a ROI that matched the PPA.
% AO
In the current analysis of the AO stimulus, we use the same AO (and AV) contrast
for all subjects. We find statistically significant bilateral clusters in nine
subjects, and one cluster in the left hemisphere of sub-09 that are within or
overlapping with the PPA ROI.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% AV
Results of the AV contrast yield homologous clusters in five subjects,
unilateral right clusters in six subjects (of which one subjects yielded a
unilateral cluster in the dedicated localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated localizer yielded
only one cluster in the right hemisphere.
% concluding statement
\todo[inline]{concluding statement that does not sound like
interpretation/discussion?}

@@

\todo[inline]{anything else to report in the following paragraph? seems more
like just an explanation of the plots}
% Bland-Altman-Plots: why they were done
To better depict/convey the agreement and difference between individual results
of the dedicated visual localizer and the primary AO contrast, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% x-axis
The x-axis of every subplot depicts the mean of $z$-values of two spatially
corresponding voxels taken from a subject's unthresholded $z$-map.
% y-axis
The y-axis of every subplot depicts the difference of $z$-values of two
spatially corresponding voxels (dedicated localizer minus AO stimulus).
% masking
Voxels were spatially constrained to a) voxels located in the occipital and
temporal lobes (gray; using the probabilistic Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
PPA overlap of all subjects (blue), and c) voxels located in the individual PPA
ROI(s)(red).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AO stimulus.

\begin{figure*} \centering
    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right). The overlays depict voxels spatially
        contrained to be located in the temporal and occipital cortex (gray),
    PPA overlap of all subjects (blue), and individual PPA (red).}
    \label{fig:bland-altman} \end{figure*}

>>>>

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort.
%
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different cognitive and perceptual
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways of processing
different kind of visual information:
% dorsal vs ventral pathway
a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
ventral pathway that leads into into the temporal lobe (the ``what pathway'')
\citep{goodale1992separate, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus is not anatomically but
functionally defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

\todo[inline]{for completeness, contrasts are mentioned in the method section.
Shall results be reported (and later discussed)?}

@@

% why individual results in the first place.
We also investigated [localization performance] of both naturalistic paradigms
on the level of individual subjects.\todo{depends on ``naturalistic stimulus for
localization''}
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
 space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (transversal
slice z=-11 for all subjects was chosen as it depicts voxels of significant
clusters in almost all subjects).
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
corrected) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection} .
% report here in group

@@

% PPA ROI (Sengupta et al., 2016)
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
clusters in 12 of 14 subjects and a unilateral right clusters in two subjects
(sub-04, sub-20) that were defined as the PPA.\todo{this is probably the part
that Simon considered as/too ``en passant''}
% procedure in Sengupta
Individual PPAs were assessed by visually inspecting unthresholded $z$-maps of
three different contrasts, and setting a subjectively best fitting $z$-threshold
to define an area in the parahippocampal gyrus [and adjacent regions of the
fusiform gyrus and anterior lingual gyrus].
% AO
In the current analysis of the AO stimulus, we use the same AO (and AV) contrast
for all subjects. We find statistically significant bilateral clusters in nine
subjects, and one cluster in the left hemisphere of sub-09 that are within or
overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% AV
Results of the AV contrast yield homologous clusters in five subjects,
unilateral right clusters in six subjects (of which one subjects yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.
% concluding statement
\todo[inline]{concluding statement that does not sound like
interpretation/discussion?}

@@

\todo[inline]{anything else to report in the following paragraph? seems more
like just an explanation of the plots}
% Bland-Altman-Plots: why they were done
To better depict/convey the agreement and difference between individual results
of the visual localizer and the primary AO contrast, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% x-axis
The x-axis of every subplot depicts the mean of $z$-values of two spatially
corresponding voxels taken from a subject's unthresholded $z$-map.
% y-axis
The y-axis of every subplot depicts the difference of $z$-values of two
spatially corresponding voxels (dedicated localizer minus AO stimulus).
% masking
Voxels were spatially constrained to a) voxels located in the occipital and
temporal lobes (gray; using the probabilistic Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
PPA overlap of all subjects (blue), and c) voxels located in individual PPA(s)
(red).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AO stimulus.

\begin{figure*} \centering
    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right).
        The overlays depict voxels spatially contrained to be located in the
        temporal and occipital cortex (gray),
        PPA overlap of all subjects (blue),
        and individual PPA(s) (red).}
    \label{fig:bland-altman} \end{figure*}
